\thesistitle

### 2019-08-25 sections/related_work.tex
Related work

\section{JDeodorant} \label{sec:jdeodorant}
The most used clone refactoring tool is JDeodorant \cite{mazinanian2016jdeodorant}. This tool is based on a set of studies, that look into several aspects of the clone refactoring process. The first of these studies is ``Refactoring Clones: An Optimization Problem'' by Krishnan et al.~\cite{krishnan2013refactoring}. The authors describe clones that are refactored by extracting their functionality to a single method. They also describe that variability between identifiers and literals have to become parameters in the extracted method. They identify the optimization problem where the variability between cloned fragments should be limited, to avoid limiting the reusability of methods because of too many method parameters. They propose an algorithm that calculates the variance between code fragments on basis of the difference in AST nodes.

@@

A study by Tsantalis et al.~\cite{tsantalis2015assessing} looks into the refactorability of code clones. This results in a set of eight preconditions to determine whether a cloned fragment is refactorable. Four of these preconditions are similar to the Krishnan et al.~\cite{krishnan2014unification} study. The following preconditions have been added:
\begin{enumerate}
  \setcounter{enumi}{4}
  %\item The parameterization of the differences between the mapped statements should not break any existing control, data, anti, and output dependencies.
  \item Matched variables having different subclass types should call only methods that are declared in the common superclass or are being overridden in the respective subclasses.
  \item The parameterization of fields belonging to differences between the mapped statements is possible only if they are not modified.
  \item The parameterization of method calls belonging to differences between the mapped statements is possible only if they do not return a void type.
  %\item The unmapped statements should be movable before or after the mapped statements without breaking existing control, data, anti, and output dependencies.
  %\item The mapped statements within the clone fragments should return at most one variable of the same type to the original methods from which they are extracted.
  \item The mapped statements within the clone fragments should not contain any conditional return statements.
  %\item The mapped branching statements (break, continue) should be accompanied with the corresponding mapped loop statements
\end{enumerate}
In our study, we simplify precondition 5 by not allowing variability in types, because of which we satisfy this precondition. We address precondition 6 by allowing modified statements as return values (and turning the calls to the extracted method into variable assignments). If more than 1 variable is assigned or other return values would be present, we flag the cloned fragments as ``not refactorable''. We address precondition 7 by using lambda expressions, which do allow void type methods to be used as parameters. We address precondition 8 by analyzing all branches in the code. If all branches return, the fragment can still be refactored even though there is a conditional return statement.

After all these studies that determine what preconditions apply to be able to refactor modified clones, the authors propose a tool named JDeodorant that helps in the process of refactoring such clones~\cite{mazinanian2016jdeodorant}. This tool takes the output of many popular clone detection tools \cite{kamiya2002ccfinder, deissenboeck2010flexible, jiang2007deckard, cordy2011nicad} and proposes refactoring opportunities. The tool is integrated in the Eclipse IDE, making it easier to directly apply the refactoring. The tool is based on previously discussed preconditions and does not allow refactorings if the preconditions are not met.

A study by Tsantalis et al.~\cite{tsantalis2017clone} looks into how lambda expressions can be used to help in the process of refactoring clones. They do this in order to mitigate some of the earlier established preconditions. Working with lambda's makes it possible to refactor statement gaps and expression differences. They find that lambda expressions are very suitable to refactor clones with variability. The authors do not discuss the impact of such refactorings on system maintainability costs, their main focus is to positively influence the refactorability of clone classes.

>>>>

\section{JDeodorant} \label{sec:jdeodorant}
The most used clone refactoring tool is JDeodorant \cite{mazinanian2016jdeodorant}. This tool is based on a set of studies, that look into several aspects of the clone refactoring process. The first of these studies is ``Refactoring Clones: An Optimization Problem'' by Krishnan et al.~\cite{krishnan2013refactoring}. The authors describe clones that are refactored by extracting their functionality to a single method. They describe that variability between identifiers and literals have to become parameters in the extracted method. They identify the optimization problem where the variability between cloned fragments should be limited, to avoid limiting the reusability of methods because of too many method parameters. They propose an algorithm that calculates the variance between code fragments on basis of the difference in AST nodes.

@@

A study by Tsantalis et al.~\cite{tsantalis2015assessing} looks into the refactorability of code clones. This results in a set of eight preconditions to determine whether a cloned fragment is refactorable. Four of these preconditions are similar to the Krishnan et al.~\cite{krishnan2014unification} study. The following preconditions have been added:
\begin{enumerate}
  \setcounter{enumi}{4}
  %\item The parameterization of the differences between the mapped statements should not break any existing control, data, anti, and output dependencies.
  \item Matched variables having different subclass types should call only methods that are declared in the common superclass or are being overridden in the respective subclasses.
  \item The parameterization of fields belonging to differences between the mapped statements is possible only if they are not modified.
  \item The parameterization of method calls belonging to differences between the mapped statements is possible only if they do not return a void type.
  %\item The unmapped statements should be movable before or after the mapped statements without breaking existing control, data, anti, and output dependencies.
  %\item The mapped statements within the clone fragments should return at most one variable of the same type to the original methods from which they are extracted.
  \item The mapped statements within the clone fragments should not contain any conditional return statements.
  %\item The mapped branching statements (break, continue) should be accompanied with the corresponding mapped loop statements
\end{enumerate}
In our study, we simplify precondition 5 by not allowing variability in types, because of which we satisfy this precondition. We address precondition 6 by allowing modified statements as return values (and turning the calls to the extracted method into variable assignments). If more than 1 variable is assigned or other return values would be present, we flag the cloned fragments as ``multiple return values'' (see Section~\ref{sec:refactorabilitysetup}). We address precondition 7 by using lambda expressions, which allow methods without return value to be used as parameters (using the \texttt{Runnable} interface). We address precondition 8 by analyzing all branches in the code. If all branches return, the fragment can still be refactored even though there is a conditional return statement.

After these studies that determine what preconditions apply to be able to refactor modified clones, the authors propose a tool named JDeodorant that helps in the process of refactoring such clones~\cite{mazinanian2016jdeodorant}. This tool takes the output of many popular clone detection tools \cite{kamiya2002ccfinder, deissenboeck2010flexible, jiang2007deckard, cordy2011nicad} and proposes refactoring opportunities. The tool is integrated in the Eclipse IDE, making it easier to directly apply the refactoring. The tool is based on previously discussed preconditions and does not allow refactorings if the preconditions are not met.

A study by Tsantalis et al.~\cite{tsantalis2017clone} looks into how lambda expressions can be used to help in the process of refactoring clones. They do this in order to mitigate some of the earlier established preconditions. Working with lambda expressions makes it possible to refactor statement gaps and expression differences. They find that lambda expressions are very suitable to refactor clones with variability. The authors do not discuss the impact of such refactorings on system maintainability, their main focus is to positively influence the refactorability of clone classes.
